---
title: "Class-11-07-real"
author: "Serhiy Sokhan"
date: "11/7/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(stringr)
library(fs)
```
# 1. Read data/ex_926_I.csv into a tibble and provide a summary.

```{r}
x_926 <- read_csv("data/ex_926_I.csv")
summary(x_926)


```

# 2. Create a vector with all the file names in data/.

```{r}
file_names <- dir_ls("data/")


```

# 3. Create a vector with just the file names that have an "A" in them.

```{r}
file_name_A <- str_subset(file_names, pattern = "A")


```

# 4. Read in all the files into one big tibble. Check out ?map_dfr . . .
# Background reading here:
# https://r4ds.had.co.nz/iteration.html#the-map-functions

```{r}
x <- map_dfr(file_names, read_csv)


```

# 5. Read in everything and also add a new variable, source, which records the
# file name from which the data came.

```{r}
prob5 <- map_dfr(file_names, read_csv, .id = "source")

```

# 6. Find the 4 files with the largest number of observations.

```{r}
prob5 %>%
  group_by(source) %>%
  tally() %>%
  arrange(desc(n)) %>%
  slice(1:4)


```

# 7. Write a function which takes a character string like "A" and then reads in
# all the files which have "A" in the name.

```{r}
files_A <- function(files, string) {
  
}


```

# 8. Create a Shiny App which displays the histogram of b, allowing the user to
# subset the display for specific values of c.

```{r}



```

